% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Timothy Soto}
\newcommand{\CVTitle}{Timothy Soto's Resume}
\newcommand{\CVNote}{CV compiled on {\today} for Acme Corporation}
\newcommand{\CVWebpage}{https://www.linkedin.com/in/timothy-soto-86b8759a/}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\noindent
\begin{tabular}[t]{@{}l}
    Cell: +1\,(979)\,492-6902 \\
    \href{mailto:tsoto@mtec.ai}
    {tsoto@mtec.ai}
\end{tabular}
\hfill% move it to the right
\begin{tabular}[t]{r@{}}
    5133 Emma Forest St. \\ Houston, Tx. 77018
\end{tabular}

\begin{Body}
    \Entry
    %%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% Objective %%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Summary}
    {Summary}
    {PDF:Summary}

    Embedded systems engineer with 8 years of experience and a wide skill-set including experience in device drivers, computer vision, and embedded linux. Proven expertise in C/C++, and hardware-software integration, with a strong track record in board bring up, thread synchronization, and performance optimization. Skilled in using GDB, Valgrind, and lab instrumentation to troubleshoot board level, ensuring robust, reliable embedded products.

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% Professional Experience %%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Professional Experience}
    {Professional Experience}
    {PDF:ProfessionalExperience}

    \SubSection
    {Mesa Engineering}
    {Houston, Texas}
    {Senior Embedded Software Engineer}
    {\DatestampYMD{2022}{06}{01} -- Present}

    \begin{Detail}
        \BulletItem
        Hands-on experience with computer vision and camera pipelines, providing an understanding of video encoding standards (e.g., H.265). This includes experience with object detection using Nvidia's Deepstream SDK, GStreamer, and YOLOv8 datasets.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Contributed to the development and integration of camera hardware subsystems, including sensor bring-up, driver development, and interface validation.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Developed frame synchronization driver and using image sensor's VSYNC signal to align frame capture with camera flashes.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Used oscilloscopes and logic analyzers to capture and analyze VSYNC/HSYNC timing behavior during sensor bring-up and debugging phases.        \vspace{1mm} %1mm vertical space
        \BulletItem
        Developed several CUDA applications to accelerate the processing of images.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Written several data parsers to support communication with I\textsuperscript{2}C, CAN, RS422/485, and ethernet connected devices.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Aided in the bring up of custom hardware that included carrier boards for Intel and Nvidia devices. In doing so I gained experience in Altium Designer, using oscilloscopes, logic analyzers, function generators, and DMMs.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Customized and maintained Buildroot-based Linux distributions for embedded platforms, streamlining system build, kernel configuration, and root filesystem generation for various hardware targets.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Used various debuggers including GDB to quickly identify and fix bugs. Leveraged Valgrind to detect memory leaks and performance bottlenecks in C/C++ applications.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Experience with the GNU tool-chain. Built a cross compiling environment to enable the development across multiple devices.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Utilized Docker to containerize embedded development environments, enabling consistent toolchains, faster onboarding for new developers, and reproducible builds across CI/CD pipelines.
        \vspace{1mm} %1mm vertical space
    \end{Detail}

    \vspace{3mm} %1mm vertical space

    \SubSection
    {HP Inc.}
    {Spring, Texas}
    {Software Engineer}
    {\DatestampYMD{2021}{03}{15} -- \DatestampYMD{2022}{06}{01}}

    \begin{Detail}
        \BulletItem
        Developer on HP's remote desktop application on Linux based systems. Added features such as clipboard sync, multi-monitor support, and dynamic resolution scaling to enhance user experience.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Ensured secure communication via TLS encryption, with optional user authentication and session timeout handling.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Assisted departments between Canonical and HP to track and resolve bugs, in order to minimize the time to resolve issues and better allocate resources.
        \vspace{1mm} %1mm vertical space
    \end{Detail}
    \vspace{3mm} %1mm vertical space

    \SubSection
    {Mesa Engineering}
    {Houston, Texas}
    {Embedded Software Engineer}
    {\DatestampYMD{2017}{05}{15} -- \DatestampYMD{2021}{03}{15}}

    \begin{Detail}
        \BulletItem
        Sole writer of an API to interface with IoT devices. This API is responsible for receiving data from devices and organize data into a SQL database. Using a LAMP (Linux, Apache, MySQL, Python) software stack, was able to comsume data from hundreds of embedded devices at once.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Successfully developed license plate reading algorithm that was 200ms faster than the previous implementation; a 20\% performance increase.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Implemented RSA encryption to validate the privacy and authenticity of sensitive data.
        \BulletItem
        Written several Linux device drivers to support custom hardware. These drivers included I$^2$C, GPIO, and a USB drivers. Also edited the Linux device tree so that these modules could be built into the kernel.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Contributed to several Verilog FPGA implementations to test time sensitive components of design.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Used various debuggers including GDB to quickly identify and fix bugs. Leveraged Valgrind to detect memory leaks and performance bottlenecks in C/C++ applications.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Experience with the GNU tool-chain. Built a cross compiling environment to enable the development across multiple devices.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Utilized Docker to containerize embedded development environments, enabling consistent toolchains, faster onboarding for new developers, and reproducible builds across CI/CD pipelines.
        \vspace{1mm} %1mm vertical space
    \end{Detail}

    \vspace{3mm} %1mm vertical space
    \pagebreak
    %\Gap
    {\textbf{U.S. Army National Guard}}
    - Fort Worth, Texas

        {\textit{Squad Leader}}
    \hfill
    \DatestampYMD{2008}{12}{15} --
    \DatestampYMD{2016}{12}{15}
    \begin{Detail}
        \BulletItem
        Operation Iraqi Freedom Veteran.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Responsible for the preparation and execution of training for a mortar squad. This included providing professional development to dozens of soldiers, peers and subordinates alike.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Consistently performed well in a high paced work environment. This involved meeting tight deadlines, comprehending new information quickly, and managing competing priorities.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Received hands-on experience in risk identification and mitigation.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Managed up to \$100,000 dollars worth of equipment. Achieved zero loss of equipment in the 4 years I spent as a squad leader.
        \vspace{1mm} %1mm vertical space
        \BulletItem
        Attended several military schools focused on leadership, effective communication, and coordination at the small team level.
    \end{Detail}
    \BigGap

    %%%%%%%%%%%%%%%
    %% EDUCATION %%
    %%%%%%%%%%%%%%%
    \Section
    {Education}
    {Education}
    {PDF:Education}

    \Entry
    \href{http://www.tamu.edu}
    {\textbf{Texas A\&M University}},
    College Station, Texas

    B.S. in
    \href{https://engineering.tamu.edu/cse/index.html}
    {Computer Engineering}
    \hfill
    \DatestampYMD{2017}{08}{15}

    %%%%%%%%%%%%%%%%%%
    %% Technical Skills %%
    %%%%%%%%%%%%%%%%%%

    \Section
    {Technical Skills}
    {Technical Skills}
    {PDF:Technical Skills}

    \noindent\begin{tabular}[t]{@{}lllllllll}
        C/C++ & Bash   & Parallel Programming & Bash & I$^{2}$C & Git      & Valgrind        \\
        GDB   & Python & Networking           & SQL  & SPI      & {\LaTeX} & RS422/485 & USB
    \end{tabular}

    %%%%%%%%%%%%%%%%%%%%%%%%%
    %% Weblinks %%
    %%%%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Weblinks}
    {Weblinks}
    {PDF:Weblinks}

    \href{https://www.linkedin.com/in/timothy-soto-86b8759a/}
    {https://www.linkedin.com/in/timothy-soto-86b8759a/} \\
    \href{https://github.com/timsoto11}
    {https://github.com/timsoto11}
\end{Body}
\end{document}
